Millions of Type Errors

### 2023-04-03 oopsla23/paper.tex
cleanup row dist

@@

\begin{figure}[t]
\begin{tabular}{rl}
 5108 total logs = 4574 nocheck + 510 nonstrict + 24 strict
 182247 total forced strict type errors, 83005 in module, 5113 in edit regions
 1521 total type errors, 1035 in module, 110 non-stx + 47 syntax in edit regions
 1146 sessions
  1143 single mode = 1046 nocheck + 94 nonstrict + 3 strict
  2 multi mode projects
  2 mode upgrades
  2 mode downgrades

 5,108 & total logs \\
       & 4,574 nocheck + 510 nonstrict + 24 strict \\
 182,247 & total forced strict type errors \\
       & {83,005 in module, 5,113 in edit regions} \\
  1,521 & total type errors \\
       & {1,035 in module, 110 non-syntax + 47 syntax in edit regions}
  \\[2ex]

>>>>

\section{Data Cleaning}

Deduplicated records with the same client timestamp,
kept only the first.
Timestamps by millisecond.

@@

\begin{figure}[t]
\begin{tabular}{rl}
 5,001 & total logs \\
       & 4,471 nocheck + 506 nonstrict + 24 strict \\
 182,247 & total forced strict type errors \\
       & {83,005 in module, 5,113 in edit regions} \\
  1,521 & total type errors \\
       & {1,035 in module, 110 non-syntax + 47 syntax in edit regions}
  \\[2ex]
